Analysis for Project

### 2021-11-11 analysis/analysis.Rmd
Panelize scatterplot
The function for making the scatterplot now takes a named list of models and then panelizes the resulting figures. It works, but things are a bit crunched and busy so I am going to keep working on alternative.

```{r}
plot_effect_scatter <- function(model) {
  coef_table <- tidy(model) %>%
    filter(str_detect(term, "race") & !str_detect(term, "Multiracial")) %>%
    mutate(term=str_remove(term, "race")) %>%
    select(term, estimate, std.error) %>%
    bind_rows(tibble(term="White", estimate=0, std.error=NA)) %>%
    mutate(multiracial=str_detect(term, "/"))

  #calculate midway points
  temp <- coef_table %>%
    filter(!multiracial) %>%
    select(term, estimate)
  means <- apply(expand.grid(temp$estimate,temp$estimate), 1, mean)
  coef_table <- expand.grid(temp$term,temp$term) %>%
    mutate(term=paste(Var1, Var2, sep="/"),
           estimate_midpoint=means) %>%
    filter(Var1!=Var2) %>%
    select(term, estimate_midpoint) %>%
    right_join(coef_table) %>%
    mutate(estimate_midpoint=ifelse(is.na(estimate_midpoint), estimate,
                                    estimate_midpoint),
           estimate=ifelse(estimate==estimate_midpoint, 0, estimate))

  ggplot(coef_table, aes(x=estimate_midpoint, y=estimate_midpoint+estimate,
                         color=multiracial,
                         ymin=estimate_midpoint+estimate-1.96*std.error,
                         ymax=estimate_midpoint+estimate+1.96*std.error))+
    geom_abline(intercept = 0, slope=1, linetype=2, color="grey70")+
   # geom_hline(yintercept = 0, linetype=2, color="grey40")+
  #  geom_vline(xintercept = 0, linetype=2, color="grey40")+
    geom_linerange(alpha=0.5)+
    geom_point()+
    geom_text_repel(aes(label=term), min.segment.length = 0)+
    theme_bw()+
    scale_color_viridis_d(end=0.6)+
    labs(x="expected log odds ratio based on midway point",
         y="actual log odds ratio")
}
```

>>>>

```{r}
plot_effect_scatter <- function(models) {
  coef_table <- models %>%
    map(function(x) {
      coefs <- tidy(x) %>%
        filter(str_detect(term, "race") & !str_detect(term, "Multiracial")) %>%
        mutate(term=str_remove(term, "race")) %>%
        select(term, estimate, std.error) %>%
        bind_rows(tibble(term="White", estimate=0, std.error=NA)) %>%
        mutate(multiracial=str_detect(term, "/"))

      #now get midpoint values
      temp <- coefs %>%
        filter(!multiracial) %>%
        select(term, estimate)
      means <- apply(expand.grid(temp$estimate,temp$estimate), 1, mean)
      coefs <- expand.grid(temp$term,temp$term) %>%
        mutate(term=paste(Var1, Var2, sep="/"),
               estimate_midpoint=means) %>%
        filter(Var1!=Var2) %>%
        select(term, estimate_midpoint) %>%
        right_join(coefs) %>%
        mutate(estimate_midpoint=ifelse(is.na(estimate_midpoint), estimate,
                                        estimate_midpoint),
           estimate=ifelse(estimate==estimate_midpoint, 0, estimate))
    }) %>%
    bind_rows(.id="model") %>%
    mutate(model=factor(model, levels=names(models)))

  ggplot(coef_table, aes(x=estimate_midpoint, y=estimate_midpoint+estimate,
                         color=multiracial,
                         ymin=estimate_midpoint+estimate-1.96*std.error,
                         ymax=estimate_midpoint+estimate+1.96*std.error))+
    geom_abline(intercept = 0, slope=1, linetype=2, color="grey70")+
    geom_linerange(alpha=0.5)+
    geom_point()+
    geom_text_repel(aes(label=term), min.segment.length = 0)+
    facet_wrap(~model)+
    theme_bw()+
    theme(legend.position = "none")+
    scale_color_viridis_d(end=0.6, direction = -1)+
    labs(x="expected log odds ratio based on midway point",
         y="actual log odds ratio")
}
```

```{r}
plot_effect_scatter(list("controls for birthplace"=model2, "+controls for parent resources"=model4))
```
